\begin{table}[H]
\small
  \captionof{table}{The resulting hit ratios over all images for different test scenarios.}
  \label{tb:result}
\begin{tabular}{l*{10}{c}r}
\hline
Parameters & Access (db1) & No access (db0) & Hard (db2) & Test images \\
\hline
Blur, $\sigma$ = 0.5  & 94\% 	& 75\% 		& 95\% 		& 50\%  \\ \hline
Blur, $\sigma$ = 1.0  & 88\% 		& 50\% 		& 84\% 	& 50\% \\ \hline
Blur, $\sigma$ = 2.5  & 19\% 	& 25\% 		& 84\% 		& 33\% \\ \hline
Tone, I = 0.5  		& 94\% 	& 100\%	 		& 95\%		& 94\% \\ \hline
Tone, I = 0.7  		& 94\%		& 100\%   	    & 95\% 	& 89\% 	\\ \hline
Tone, I = 1.3  		& 75\%		& 75\%		& 87\% 	& 61\% 	 \\ \hline
Scale, s = 0.9 		& 100\% 		& 50\% 		& 95\% 	& 94\% 	 \\ \hline
Scale, s = 1.1  		& 100\% 		& 100\% 		& 97\% 	& 94\%		  \\ \hline
Scale, s = 2  			& 100\% 		& 50\%		& 97\% 	& 50\%		  \\ \hline
Rotation, $\theta$ = 5$^{\circ}$  	& 94\% 	& 75\%		& 97\% 		& 78\% 	 \\ \hline
Rotation, $\theta$ = 10$^{\circ}$   & 94\% 	& 75\%		& 95\% 		& 78\% 	 \\ \hline
Rotation, $\theta$ = 20$^{\circ}$  & 88\% 		& 50\%		& 95\% 	& 72\% 	 \\ \hline
\end{tabular}
\end{table}

A large test batch were performed to test different types of image problems and conditions. The tested conditions include varying illumination, scale, rotation and blur. All cases were individually reviewed in order to determine a hit, meaning that the face is extracted correctly. Furthermore were the blur tests done by using a Gaussian low pass filter while varying the standard deviation parameter $\sigma$.
The tone level tests were done by decreasing or increasing the intensity value at each pixel with a global percentage parameter I. For example $I = 0.5$ corresponds to decrease the intensity of the image with 50\%.
More over were all images rotated with an angle $\theta$ and scaled with a percentage parameter $s$.
\newline
\indent Table \ref{tb:result} presents the hit ratio for the face detection with different types of test images and databases.
The images in the database \textit{Access} are persons with access permissions and with different types of background environments.
\textit{No access} images picture persons that should not be granted access. The original images have homogeneous intensities and backgrounds.
The database \textit{Hard} has images with highly varying backgrounds and illumination conditions. Finally, \textit{Test images} is a collection of randomly selected images with various conditions.
